Constrained Circulation Ensemble

### 2025-11-10 ms/cce.tex
Updates from Overleaf

\draftfalse
\journalname{Geophysical Research Letters}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  TITLE
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Constrained Circulation Ensemble}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  AUTHORS AND AFFILIATIONS
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\authors{D. Kennedy\affil{1,2}, D. M. Lawrence\affil{1}, I. R. Simpson\affil{1}}
\affiliation{1}{Climate and Global Dynamics Laboratory, NSF-NCAR}
\affiliation{2}{Earth Research Institute, University of California Santa Barbara}
\correspondingauthor{Daniel Kennedy}{djk2120@ucar.edu}

@@

\begin{abstract}
[ enter your Abstract here ]
\end{abstract}

\section*{Plain Language Summary}
Enter your Plain Language Summary here or delete this section.
Here are instructions on writing a Plain Language Summary: 
https://www.agu.org/Share-and-Advocate/Share/Community/Plain-language-summary

@@

Water in the Southwest United States (SWUS) is somewhat scarce, but also has myriad productive uses including agriculture, public water supply, recreation, and supporting the local ecology.
Likewise the abundance/scarcity of water is strongly related to fire risk and temperature extremes. 
Climate change has added strain to the water supply, with drier air and reduced snowpack due to warming, as well as increased precipitation variability.
The summer of 2020 was the driest of the meteorological record within the SWUS \cite{mankin2021,hoell2022} and arrived in the midst of a 22-year megadrought (2000-2021), which was drier than any other extended drought in a soil moisture reconstruction dating back to 800 C.E. \cite{williams2022}.
One more sentence about the effects of the 2020 drought tk, e.g. water shortage and temperature extremes.

@@

For this study we utilized the Community Earth System Model, version 2 (CESM2) \cite{danabasoglu2020}.
We ran a suite of simulations in land-atmosphere coupled mode (namely the FHIST\_BGC component set) using a data ocean (simulations described in Section \ref{sect:exp}).
We compared our simulations to the CESM2 large ensemble (CESM2-LE) \cite{rodgers2021}, which consists of 100 transient simulations (1850-2100) of the fully coupled configuration of CESM2.
The simulations follow historical forcing through 2014 and then switch to the SSP3-7.0 emissions scenario.
This ensemble is useful, because it provides a large number of model realizations, sampling across a range of internal climate variability states.
For the sake of comparison, we have utilized the CESM2-LE codebase for our simulations and the same forcing where applicable.

>>>>

\draftfalse
\journalname{Geophysical Research Letters}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  TITLE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Constrained Circulation Ensemble}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  AUTHORS AND AFFILIATIONS
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authors{D. Kennedy\affil{1,2}, D. M. Lawrence\affil{1}, I. R. Simpson\affil{1}}
\affiliation{1}{Climate and Global Dynamics Laboratory, NSF-NCAR}
\affiliation{2}{Earth Research Institute, University of California Santa Barbara}
\correspondingauthor{Daniel Kennedy}{djk2120@ucar.edu}

@@

\begin{abstract}
TKTK
\end{abstract}

\section*{Plain Language Summary}
TKTK

@@

Water in the Southwest United States (SWUS) is scarce, but also has myriad productive uses including agriculture, public water supply, recreation, and supporting the local ecology.
Likewise the abundance of water is strongly related to fire risk and temperature extremes. 
Climate change has added strain to the water supply, with drier air and reduced snowpack due to warming, as well as increased precipitation variability.
The summer of 2020 was the driest of the meteorological record within the SWUS \cite{mankin2021,hoell2022} and arrived in the midst of a 22-year megadrought (2000-2021), which was drier than any other extended drought in a soil moisture reconstruction dating back to 800 C.E. \cite{williams2022}.
One more sentence about the effects of the 2020 drought tk, e.g. water shortage and temperature extremes.

@@

For this study we utilized the Community Earth System Model, version 2 (CESM2) \cite{danabasoglu2020}.
We ran a suite of simulations in land-atmosphere coupled mode (namely the FHIST\_BGC component set) using a data ocean (simulations described in Section \ref{sect:exp}).
We compared our simulations to the CESM2 large ensemble (CESM2-LE) \cite{rodgers2021}, which consists of 100 transient simulations (1850-2100) of the fully coupled configuration of CESM2.
The simulations follow historical forcing through 2014 and then switch to the SSP3-7.0 emissions scenario.
This ensemble is useful, because it provides a large number of model realizations, sampling across a range of internal climate variability states.
For the sake of comparison, we utilized the CESM2-LE codebase for our simulations and the same forcing where applicable.
